Specification and Verification of Stencil Computation Shape

### 2016-11-15 paper.tex
Typos

It should be noted that our verification tool does not deal in the
class of bugs that can be detected automatically (\emph{push-button
  verification}). Instead, stencil computation bugs must be
identified relative to a specification of the intended behaviour.

@@

\item We give a detailed verification case study of two
  particular stencil computation commonly used in scientifc computing,
  simulating programming errors. Our approach is able to detect all
  possible indexing errors for these computations.
\end{itemize}
%

>>>>

It should be noted that our verification tool does not target the
class of bugs that can be detected automatically (\emph{push-button
  verification}). Instead, stencil computation bugs must be
identified relative to a specification of the intended behaviour.

@@

\item We give a detailed verification case study of two
  particular stencil computations commonly used in scientifc computing,
  simulating programming errors. Our approach is able to detect all
  possible indexing errors for these computations.
\end{itemize}
%
